To Be Decided

### 2025-07-22 paper/main.tex
Finish Section IV-A-2
More things written

        For all experiments, the following common parameters were used: $\lambda_b$ = 1 m, noise level = 5\%, relative permittivity of the background medium $\epsilon_{rb}$ = 1, and incident wave amplitude = 1 V/m. Data synthesis was performed using the MoM-CG-FFT algorithm \cite{su1987calculation} with 5000 iterations.

@@

            In all instances, the dimensions of the DoI were set to $2\lambda_b\times2\lambda_b$, and the measurement points' distance radius $R_O$ was fixed at $4\lambda_b$.

@@

                The first case study was designed to evaluate the applicability of the proposed indicator in a straightforward scenario where various algorithms could be applied. This case study features a scatterer shaped like a five-pointed star, centrally positioned within the image. This choice was made to select a geometry that, while symmetric and well-defined, has more vertices compared to more common shapes such as squares or triangles. The contrast was set to 0.25, and the radius from the center of the scatterer to the farthest vertices was set to 0.9$\lambda_b$. A total of 80 measurement points ($N_M$) and 80 incidence angles ($N_S$) were used. Under these conditions, the Degree of Nonlinearity (DNL) for the test is 0.12, which is significantly lower than the threshold beyond which the Born Approximation becomes inapplicable, i.e., 1 \cite{bucci2001degree}. The scattered field was synthesized using a discretization of 120$\times$120 pixels for the original image, and all reconstructions were performed using a discretization of 40$\times$40 pixels.

@@

                \begin{table}[!htb]
                    \centering
                    \renewcommand{\arraystretch}{1.5}
                    \caption{Results for the single scatterer case study.}
                    \label{tab:star}
                    \begin{tabular}{cccccc}
                        Method & LSM & OSM & BIM & CSI & SOM \\\hline
                        $\zeta_S$ (\%) & 29.2 & 24.5 & 14.9 & 26.3 & 15.4 \\
                    \end{tabular}   
                \end{table}

@@

                {\color{red} EU PRECISO RODAR NOVAMENTE O EXPERIMENTO PORQUE O NÚMERO DE MEDIÇÕES E FONTES NÃO FORAM IGUAIS NA PRIMEIRA VEZ.}

@@

            An exception would be algorithms that solve the imaging problem as an optimization problem, where the decision variables are the position, vertices (or other characteristics of a predefined geometry), and contrast of the scatterers \cite{michalski2000electromagnetic,salucci2022learned,zardi2025physics}. Additionally, in scenarios involving strong scatterers, traditional methods generally struggle to recover scatterer geometry effectively due to the increased problem hardness. In such scenarios, studying position detection becomes more relevant.

@@

            Considering this, the experiments in this section were designed for scenarios involving strong scatterers, where traditional methods cannot adequately recover scatterer geometry. Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.

@@

@@

>>>>

        % For all experiments, the following common parameters were used: $\lambda_b$ = 1 m, noise level = 5\%, relative permittivity of the background medium $\epsilon_{rb}$ = 1, and incident wave amplitude = 1 V/m. Data synthesis was performed using the MoM-CG-FFT algorithm \cite{su1987calculation} with 5000 iterations. A total of 80 measurement points ($N_M$) and 80 incidence angles ($N_S$) were used. The dimensions of the DoI were set to $2\lambda_b\times2\lambda_b$, and the measurement points' distance radius $R_O$ was fixed at $4\lambda_b$. All reconstructions were performed using a discretization of 40$\times$40 pixels.

        For all experiments, the following common parameters were used: background wavelength $\lambda_b = 1$ m, noise level of 5\%, relative permittivity of the background medium $\epsilon_{rb} = 1$, and incident wave amplitude of 1 V/m.

        Data synthesis was performed using the MoM-CG-FFT algorithm \cite{su1987calculation} with 5000 iterations. The measurement configuration consisted of 80 measurement points ($N_M$) and 80 incidence angles ($N_S$), with measurement points arranged in a circular array at distance $R_O = 4\lambda_b$ from the DOI center.

        The DOI dimensions were set to $2\lambda_b \times 2\lambda_b$, and all reconstructions were performed using a $40 \times 40$ pixel discretization.

@@

@@

                The first case study was designed to evaluate the applicability of the proposed indicator in a straightforward scenario where various algorithms could be applied. This case study features a scatterer shaped like a five-pointed star, centrally positioned within the image. This choice was made to select a geometry that, while symmetric and well-defined, has more vertices compared to more common shapes such as squares or triangles. The contrast was set to 0.25, and the radius from the center of the scatterer to the farthest vertices was set to 0.9$\lambda_b$. Under these conditions, the Degree of Nonlinearity (DNL) for the test is 0.12, which is significantly lower than the threshold beyond which the Born Approximation becomes inapplicable, i.e., 1 \cite{bucci2001degree}. The scattered field was synthesized using a discretization of 120$\times$120 pixels for the original image.

@@

                \begin{table}[!htb]
                    \centering
                    \renewcommand{\arraystretch}{1.5}
                    \caption{Shape recovering study, single scatterer: shape error indicator $\zeta_S$ for each algorithm.}
                    \label{tab:star}
                    \begin{tabular}{cccccc}
                        Method & LSM & OSM & BIM & CSI & SOM \\\hline
                        $\zeta_S$ (\%) & 29.2 & 24.5 & 14.9 & 26.3 & 15.4 \\
                    \end{tabular}   
                \end{table}

@@

@@

            An exception would be algorithms that solve the imaging problem as an optimization problem, where the decision variables are the position, vertices (or other characteristics of a predefined geometry), and contrast of the scatterers \cite{michalski2000electromagnetic,salucci2022learned,zardi2025physics}. Additionally, in scenarios involving strong scatterers with small size compared to the wavelength, traditional methods generally struggle to recover scatterer geometry effectively due to the increased problem hardness. In such scenarios, studying position detection becomes more relevant.

@@

            Considering this, the experiments in this section were designed for scenarios involving strong scatterers with small size, where traditional methods cannot adequately recover scatterer geometry. Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios. In addition, the DOI discretization for data synthesis was performed using a finer grid with $160 \times 160$ pixels.

            Considering this, the experiments in this section were designed for scenarios involving strong scatterers with small dimensions, where traditional methods cannot adequately recover scatterer geometry. Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.

            For all subsequent experiments, LSM was removed and an other method was introduced. Since the analytical solution for scattering from an infinite dielectric cylinder is well-established \cite{harrington2001time}, it becomes possible to determine the optimal circular approximation (defined by radius, position, and contrast) that best fits the scattered field of any single scatterer.

            To optimize these four parameters, we employ a two-stage approach \cite{virtanen2020SciPy}:
            \begin{enumerate}
                \item Global optimization: The Differential Evolution (DE) algorithm \cite{storn1997differential} with 50 generations, 15 individuals, crossover rate of 0.7, and mutation factor ranging from 0.5 to 1.
                \item Local refinement: The L-BFGS-B algorithm \cite{zhu1997algorithm} for improved accuracy.
            \end{enumerate}

            While DE is inherently stochastic and would typically require multiple executions for robust analysis, the problem structure and subsequent refinement step allow for single execution per instance based on previous experimental validation. This methodology is referred to as Circle Approximation (CA) throughout this work.

            It should be noted that \cite{michalski2000electromagnetic} employed a similar DE-based approach for circular fitting, though their work focused specifically on perfect electric conductor cylinders under cylindrical scatterer assumptions.

@@

                The first scenario for studying the position indicator utilized a star-shaped scatterer, similar to the experiments described in Sections \ref{sec:results:shape:star} and \ref{sec:results:shape:varying}. However, this configuration featured the scatterer positioned in the upper-right corner and rotated by 30 degrees, as illustrated in Fig. \ref{fig:position:single:ground_truth}. The scatterer contrast was set to 7, while the radius from the center to the farthest vertices was reduced to 0.15$\lambda_b$. Under these configurations, the DNL for this experiment reaches 1.7, which is slightly above the threshold of 1.

                % A Fig. \ref{fig:position:single:recons} mostra as imagens reconstruídas por cada algoritmo. Conforme esperado, uma vez que o contraste é alto e o tamanho do espalhador é pequeno, os métodos vão reconstruir pequenos borrões na região no espalhador. A maneira como esses borrões são reconstruídos é importante, visto que essa informação impacta na medição da posição do espalhador. Tendo isto em vista, o CSI foi quem teve a maior dificuldade na reconstrução, uma vez o contraste se concentrou em uma região muito pequena e que o nível de contraste foi bem baixo se comparado aos demais métodos quantitativos. Nota-se também que o CA foi quei mais se aproximou do contraste do espalhador.

                Fig. \ref{fig:position:single:recons} shows the images reconstructed by each algorithm. As expected, given the high contrast and small scatterer size, the methods reconstruct small blobs in the scatterer region. The way these blobs are reconstructed is relevant, as this information directly impacts the measurement of scatterer position.

                In this regard, CSI experienced the greatest reconstruction difficulty, with contrast concentrated in a very small region and significantly lower contrast levels compared to the other quantitative methods. It is also notable that CA most closely approximated the actual scatterer contrast.

                \begin{figure*}[!htb]
                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/0.eps}\label{fig:position:single:ground_truth}}
                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/1.eps}}
                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/2.eps}} \\
                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/3.eps}}
                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/4.eps}}
                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/5.eps}}
                    \caption{Position detection study, single scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:position:single:recons}
                \end{figure*}

                Table \ref{tab:position:single:zeta_p} summarizes the results of the position error indicator for each algorithm. The results indicate that OSM, BIM, and CA achieved the best performance, while SOM performed similarly. The largest error was observed for CSI, which, due to its greater difficulty in quantifying the object's contrast, had more difficulty in capturing the object's position. Generally, the position detection errors for most algorithms were low. However, there may be applications where precision in position detection is critical, such as in tumor detection, for example.

                \begin{table}[!htb]
                    \centering
                    \renewcommand{\arraystretch}{1.5}
                    \caption{Position detection study, single scatterer: position error indicator $\zeta_P$ for each algorithm.}
                    \label{tab:position:single:zeta_p}
                    \begin{tabular}{cccccc}
                        Method & OSM & BIM & CSI & SOM & CA \\\hline
                        $\zeta_P$ (\%) & 0.08 & 0.04 & 4.68 & 0.53 & 0.04 \\
                    \end{tabular}   
                \end{table}

@@

                % Embora o indicador proposto para mensurar o erro na posição tenha sido pensado para cenários com um único espalhador, ele também pode ser aplicado em cenários com múltiplos espalhadores. Nestes casos, o centróide do arranjo como um todo é o ponto de referência para a medição do erro na posição. Este tipo de investigação pode ser útil para aplicações como through-wall imaging, por exemplo.

                Although the proposed indicator for measuring position error was designed for scenarios with a single scatterer, it can also be applied in scenarios with multiple scatterers. In these cases, the centroid of the arrangement as a whole serves as the reference point for measuring position error. This type of investigation can be useful for applications such as through-wall imaging, for example.

                Baseado nisto, neste experimento são considerados três espalhadores: a estrela

                % Based on this approach, this experiment considers three scatterers: the star-shaped object from the previous study, a circular scatterer, and a square scatterer. All objects have a contrast of 7 and are positioned at different locations within the DOI to create a challenging multi-target scenario. The goal is to evaluate how well each algorithm can detect the overall position of the scatterer arrangement when individual object geometries cannot be accurately recovered.

                % Fig. \ref{fig:position:multiple:recons} shows the reconstructions obtained by each algorithm for the multiple scatterer scenario. As expected in this high-contrast, small-size configuration, the algorithms reconstruct blob-like structures rather than distinct object geometries. The quality and positioning of these reconstructed features directly influence the centroid calculation and, consequently, the position error measurement.

                % Table \ref{tab:position:multiple:zeta_p} presents the position error results for each algorithm. Interestingly, CSI achieved the best performance in this multi-scatterer scenario, despite its poor performance in the single scatterer case. This suggests that the algorithm's behavior may be different when dealing with multiple targets. BIM and SOM showed similar intermediate performance, while OSM and CA exhibited higher position errors, indicating greater difficulty in accurately localizing the overall scatterer arrangement.

                \begin{figure*}[!htb]
                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/0.eps}\label{fig:position:multiple:ground_truth}}
                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/1.eps}}
                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/2.eps}} \\
                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/3.eps}}
                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/4.eps}}
                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/5.eps}}
                    \caption{Position detection study, multiple scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:position:multiple:recons}
                \end{figure*}

                \begin{table}[!htb]
                    \centering
                    \renewcommand{\arraystretch}{1.5}
                    \caption{Position detection study, multiple scatterers: position error indicator $\zeta_P$ for each algorithm.}
                    \label{tab:position:multiple:zeta_p}
                    \begin{tabular}{cccccc}
                        Method & OSM & BIM & CSI & SOM & CA \\\hline
                        $\zeta_P$ (\%) & 10.24 & 8.30 & 4.86 & 8.27 & 12.85 \\
                    \end{tabular}   
                \end{table}
